---
title: "sys.nframe()"
author: "jim"
date: 2020-07-23T21:13:14-05:00
categories: ["R"]
tags: ["R Markdown", "plot", "regression"]
---

```{r setup, eval = FALSE , include=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
library(jimTools)
library(blogdown)
library(rmarkdown)

# knitr::knit_exit()
```

```{r nframe, eval = FALSE  }
getwd()
blogdown::hugo_version()
# for 32-bit, must use extended = FALSE
blogdown::install_hugo(extended = FALSE)
blogdown::serve_site()
blogdown::stop_server()

blogdown::remove_hugo(version='all')
```
In prior post, used ls() to list objects in a environment.   Often the
environment is .global_env() but when a function is called it executes in its
own environment.


Here we see what happens when one function calls another and we examine 
sys.nframe()


AAA How many levels down ?  0=GlobalEnv
```{r nframe_levels}
parentls <- function() {
  cat("nframe = ", sys.nframe() , "\n")
}


a  <- function() {
  cat("nframe = ", sys.nframe() , "\n")
  b()
}

b   <- function(){ 
  cat("nframe = ", sys.nframe() , "\n")
  c()
}

c  <- function(){ 
  cat("nframe = ", sys.nframe() , "\n")
}


cat("nframe = ", sys.nframe() , "\n")
a() # objects in a's environment

f  <- function() a()
f()
```
recursive!
sys.nframe()
blogdown has trouble  Cstack; 
```{r loop, eval=FALSE, include=FALSE   }
cat("nframe = ", sys.nframe() , "\n")
a  <- function() {
  if (sys.nframe() == 9) return()
  cat("nframe = ", sys.nframe() , "\n")
  a()
}
a()
# knitr::knit_exit()
```

```{r render, eval=FALSE  }
rmarkdown::render(
   "/home/jim/code/hugo_projects/blog/content/post/0001_nframe.Rmd", 
   output_format = "pdf_document",
   output_file= "~/Downloads/print_and_delete/out.pdf")
```


old
AAA Example:   objects in calling env() (or parent.frame())
https://stackoverflow.com/questions/28641395/what-is-parent-frame-of-r
```{r main}
# objects in parent.frame (calling env)
parentls <- function() {
  ls(envir = parent.frame())
}

a<-function() {
    x <- 5
    parentls()
}

b <- function() {
    z <- 10
    parentls()
 }

a() # objects in a's environment
b()
parentls()
```
