---   
title: "`r knitr::current_input()`"
date: "`r paste('last updated', 
    format(lubridate::now(), ' %d %B %Y'))`"
output:   
  pdf_document:   
    latex_engine: xelatex
  html_document:  
        code_folding:  show
        toc: true 
        toc_depth: 2
        toc_float: true
fontsize: 11pt 
geometry: margin=0.5in,top=0.25in 
---


Exploring R base functions related to enviroment.

This is meant as examples of use, and NOT as a tutorial or explanation of R's
environmental structure.   Others do this much better:  
  -   

```{r setup, include=FALSE		}
knitr::opts_chunk$set(echo = TRUE,
                      comment = "      ##",
                      error = TRUE,
                      collapse = TRUE)
```


```{r library, include=FALSE		}
library(jimTools)
``` 

ls() returns objects in character vector.
```{r simple}
x  <- 2
y  <- 2*x
ls()
knitr::knit_exit()
```

ls() includes name of functions.
```{r add_fun}
ls()
f  <- function() {
  z  <- 2
}

ls()  # includes f
```

environment is ....
environment() returns <env>, one of R's typeof
```{r}
environment()
typeof(environment())
```

in fact,  R has a whole tree of environments
search
```{r search}
search()
```

objects inside a package
```{r}

# 1st 9
ls(envir=as.environment("package:usethis"))[1:9]
```




ls(envir=as.environment("package:usethis"))
And you can add your own, sometimes R creates its won.

Example, Modify f 
```{r modify_f}
ls()

f  <- function() {
  z  <- 2
  print(environment())
  print(ls())
}

ls()  # includes f and g

```

```{r f}
f()
```




```{r knit_exit(), eval= FALSE    } 
knitr::knit_exit()
```

\newpage

```{r render, eval=FALSE, include=F	} 
{
file  <- "00_ls_objects.Rmd"
file  <- here(file)
file
}

rmarkdown::render(file,
                  output_format= "html_document")
```

