--- 
title: "ls_objects"  
date: "`r paste('last updated', 
    format(lubridate::now(), '%H:%M, %d %B %Y'))`"  
output: 
  pdf_document: 
    latex_engine: xelatex
toc: TRUE 
toc_depth:  1 
fontsize: 12pt 
geometry: margin=0.5in,top=0.25in 
---


Exploring R base function related to enviroment.

This is meant as examples of use, NOT as a tutorial or explanation of R's
environmental structure.   Others do this much better:  
  -   

```{r setup, include=FALSE		}
knitr::opts_chunk$set(echo = TRUE,
                      comment = "      ##",
                      error = TRUE,
                      collapse = TRUE)
```


```{r library, include=FALSE		}
library(jimTools)
``` 

ls() returns objects in character vector.
```{r simple}
ls()  <- NULL
x  <- 2
y  <- 2*x
ls()
```

ls() includes name of functions.
```{r add_fun}
ls()
f  <- function() {
  z  <- 2
}

ls()  # includes f
```

environment is ....
environment() returns <env>, one of R's typeof
```{r}
environment()
typeof(environment())
```

in fact,  R has a whole tree of environments
search
```{r search}
search()

```

objects inside a packagea
```{r}

# 1st 9
ls(envir=as.environment("package:usethis"))[1:9]
```




ls(envir=as.environment("package:usethis"))
And you can add your own, sometimes R creates its won.

Example, Modify f 
```{r modify_f}
ls()

f  <- function() {
  z  <- 2
  print(environment())
  print(ls())
}

ls()  # includes f and g

```

```{r f}
f()
```




```{r knit_exit(), eval= FALSE    } 
knitr::knit_exit()
```

/newpage

```{r render, eval=FALSE	} 
file  <- "0000_ls_objects.Rmd"
rmarkdown::render(file,
                  output_dir="~/Downloads/print_and_delete")
```

